Robust Deluding Adversarial Examples

### 2019-05-04 minutia/paper.tex
Updates from Overleaf

\subsection{Objective}
The ultimate goal is deceiving the model either in choosing the worst possible action in an RL task or misclassifying an input in a classification task in a way which is not perceptible for unaided eye. In terms of a Markovian RL task we show how minimum set of worst-case actions are needed to result in the minimum final reward.

@@

>>>>

\subsection{Objective}
The ultimate goal is deceiving the model either in choosing the worst possible action in an RL task or misclassifying an input in a classification task in a way which is not perceptible for unaided eye. In terms of a Markovian RL task we show how minimum set of worst-case actions are needed to result in the minimum final reward. We try to show that the model is not robust to other configuration of each benchmarks with different dynamics.

@@

\subsection{Reward Perturbation Attacks}
In an adversarial environment we try to perturb reward to interfere in learning process of the RL agent. We considered this attack also in scenarios with a single reward which we will show the process later.
